Ornaments as indicators of social changes and cultural practices in northeast Taiwan before and after European colonial period

### 2019-12-09 analysis/paper/paper.Rmd
change the code order

```{r C14-table-data}
kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))
cal_kw_dates <- readr::read_csv(here("analysis", "data", "raw_data", "kwl_cal_dates.csv"))

knitr::kable(table_kw_dates,
             caption = "Radiocarbon dates on charcoals from Kiwulan (Chen 2007). Recalibrated using IntCal13 Atmospheric curve.")
```

@@

@@

>>>>

@@

kw_dates <- readxl::read_excel(here("analysis", "data", "raw_data", "KWL_C14_dates.xlsx"))

@@

```{r C14-table-data}
cal_kw_dates <- readr::read_csv(here("analysis", "data", "raw_data", "kwl_cal_dates.csv"))

knitr::kable(table_kw_dates,
             caption = "Radiocarbon dates on charcoals from Kiwulan (Chen 2007). Calibrated using IntCal13 Atmospheric curve.")
```
